Dark matter halo shapes at $z=0$ in the Auriga simulations

### 2019-07-21 Document/paper.tex
edit

In Figure \ref{fig:alignment_correlations} we already showed that this
correlation strongly depends on radius, we conclude that high
triaxiality values cannot be the full explanation.
Furthermore the twisting happens in such a way that it allows an
almost perfect alignment between the stellar disc at $0.1R{200}$ and
the halo shape measured at $0.25R_{200}$

@@

Our Figure \label{fig:observations} shows an explicit comparison in
the $c/a$-$b/a$ plane of our results in MHD simulations against the
results by LM10 and BBFK16.  
We find six MHD halos with $b/a<0.93$ and $c/a>0.77$ that could be
considered consistent with their shape constraints  by BBFK16, while
only one outlier DMO halo is consistent with those constraints.
In contrast, none of the simulated halos (MHD nor DMO) is consistent
with the LM10 results. 
The change of triaxility with radius in our simulations cannot account
for these two extremely different shape constraints at different
radii.

The results by LM10 could then place the dark matter halo of our Milky
Way as an extreme outlier in the $\Lambda$ CDM model. 
This extreme prolateness also correlates with the extreme
triaxiality of the 11 classical satellites of the MW ($c/a\approx
0.2$, and $b/a\approx0.9$) with an spatial distribution 
also oriented perpendicular to the MW plane, another highly unusual
feature in the $\Lambda$ CDM model \citep{2018MNRAS.478.5533F}.

@@

A more complete understading of the influence of baryons on the
different properties we have measured will require two elements, at
least. First, an study on how the halo and the disc co-evolved as a
function of time. Second, a calibrating the effect of the cosmic web
(both dark matter and gaseous) on any evoluionary trend
\citep{2014MNRAS.443.1090F,2017MNRAS.469..594B,2019MNRAS.487.1607G} 
We finalize by suggesting that the twisting density shells we find in
some of the halos is feature that deserves to be explored in the
process of constraining shape parameters from tidal stream data.  The
inclusion of a parameterization describing this degree of twisting
might relax the conflict between the observational constraints and the
numerical results.

>>>>

@@

Figure \ref{fig:observations} shows an explicit comparison in
the $c/a$-$b/a$ plane of our results in MHD simulations against the
results by \cite{LM10} and \cite{Bovy16}.
We find six MHD halos with $b/a<0.93$ and $c/a>0.77$ that could be
considered consistent with their shape constraints  by \cite{Bovy16}, while
only one outlier DMO halo is consistent with those constraints.
In contrast, none of the simulated halos (MHD nor DMO) is consistent
with the results \cite{LM10}. 
The change of triaxility with radius in our simulations cannot account
for these two extremely different shape constraints at different
radii.

The results by \label{LM10} could then place the dark matter halo of our Milky
Way as an extreme outlier in the $\Lambda$CDM model. 
This extreme prolateness also correlates with the extreme triaxiality
of the 11 classical satellites of the MW ($c/a\approx 0.2$, and
$b/a\approx0.9$) measured at larger radii, with an spatial
distribution  also oriented perpendicular to the MW plane, another
highly unusual feature in the $\Lambda$CDM \citep{2018MNRAS.478.5533F}.

@@

A more complete understading of the influence of baryons on the
different properties we have measured will require at least two more elements.
First, an study on how the halo and the disc co-evolved as a
function of time. Second, a calibrating the effect of the cosmic web
(both dark matter and gaseous) on any evoluionary trend
\citep{2014MNRAS.443.1090F,2017MNRAS.469..594B,2019MNRAS.487.1607G} 
We finalize by suggesting that the twisting density shells we find in
some of the halos is feature that deserves to be explored in the
process of constraining shape parameters from tidal stream data.  The
inclusion of a parameterization describing this degree of twisting
might relax the conflict between the observational constraints and the
numerical results.
